\LARGE \bf Artifical Cognition for Social Human-Robot Interaction:\\ An Implementation

### 2016-06-16 paper.tex
Even more polish on the timeline figure
Added a summary of the paper

        \path (-0.5,0) edge (figbottom) node[sloped, above left, rotate=90] {time};

        \fill[gray!10!white] (4.6,.5) rectangle (figbottom);
        \node at (2,0) (percept) {\bf Perception};
            \node[below=0.5 of percept.south west, anchor=mid] {camera};
            \node[below=0.5 of percept.south east, anchor=mid] {3D model};

@@

        \fill[gray!10!white] (11.5,.5) rectangle (16.5,-28.5);
        \node[right=4 of kb] (plan) {\bf Plan};
            \node[below=0.5 of plan.south west, anchor=mid east] (probot) {robot};
            \node[below=0.5 of plan.south east, anchor=mid west] (phuman) {human};
            \draw[dotted] (probot) to (figbottom -| probot);
            \draw[dotted] (phuman) to (figbottom -| phuman);

@@

>>>>

        \fill[gray!10!white] (4.6,.5) rectangle (figbottom);

        \path (-0.5,0) edge (figbottom) node[sloped, above left, rotate=90] {\large\bf time};

        \node at (2,0) (percept) {\bf Perception};
            \node[below=0.5 of percept.south west, anchor=mid] {camera};
            \node[below=0.5 of percept.south east, anchor=mid] {3D model};

@@

        \fill[gray!10!white] (12,.5) rectangle (17,-28.5);
        \node[right=4.5 of kb] (plan) {\bf Plan};
            \node[below=0.5 of plan.south west, anchor=mid east] (probot) {robot};
            \node[below=0.5 of plan.south east, anchor=mid west] (phuman) {human};
            \draw[dotted] (probot) to (figbottom -| probot);
            \draw[dotted] (phuman) to (figbottom -| phuman);

@@

\section{Conclusion}
\label{sect|conclusion}

\subsection{Summary of the Contribution}

We have presented in this paper a large deliberative architecture designed for
social robots. While most of its sub-components have been independently
presented in other publications, we offer here for the first time a perspective
on the overall integration of these components into a coherent and consistent
system for social human-robot interaction. We have first exposed our underlying
knowledge model based on Description Logics~\cite{Lemaignan2010} and some of the
resulting reasoning capabilities pertaining to disambiguation~\cite{Ros2010b}
and mental modelling~\cite{warnier2012when} that are shown to effectively
scaffold interaction using human-level semantics and cognitive skills. We have
then presented our approach to symbol grounding, build on an amodal situation
assessment environment~\cite{Sisbot2011} that supports perspective
taking~\cite{Marin2008,Ros2010}. We
combine it further with an advanced natural
language processor~\cite{Lemaignan2011a} to provide complete multi-modal interactive
communication.  The paper also covers our symbolic social task
planner~\cite{Alili2008, Alili2009, Lallement2014}: it generates predictive
plans of the human actions that enable the system to plan for joint human-robot
tasks. It can also make use of social heuristics to optimize plans for social
acceptability. We briefly mention our human-aware motion and manipulation
planner~\cite{Sisbot2008,Mainprice2011,Pandey2011}, and finally present two
execution controller, the PRS-based {\sc Shary}~\cite{clodic2008shary,fiore2014} and the
event-driven {\sc pyRobots}~\cite{lemaignan2015pyrobots}.

The integration of these components in a consistent, working and observable
system is supported by the design of our software interfaces: most of the
datastreams exchanged by our components uses high-level semantics in the form of
first-order logic statements. The two reported support studies further evidence
how our use of explicit, high-level semantics provide a low-impedance,
human-level mean of building a complex deliberative
architecture for socially interactive robots~\cite{Lemaignan2013}.

\subsection{A Deliberative Architecture for Social Robots}

Rachid -- TDB: what are the other 'deliberative architecture for socially interactive
robots' and where/how ours is better?

Discussion on deliberative architectures != cognitive architecture: a \emph{cognitive
architecture} is usually understood as an artificial yet principled model of (human)
cognition, while we propose a practical approach to consistently combine a large
set of independent cognitive processes by bridging them through high-level semantics.
